Direct observation of \swave scattering of fermions crossing a Feshbach resonance

### 2015-02-24 draft1.tex
Fixed formatting in figues through figure 9.
Still need attention: fig. 7 - should add a plot of average velocity and
position? They are roughly indistinguishable for both cloud widths, but
not sure how to fit it in.

fig 9. - add signal to noise graph as per Ian's suggestion?

	\subfigure[]{\includegraphics*[scale=0.4]{Picture1c}}

@@

	\includegraphics*[scale=0.57]{figure1}

@@

	\includegraphics[scale=0.57]{figure2}

@@

	\includegraphics[scale=0.57]{figure3}
\caption{Optical densities as a function of probe intensity as predicted by the simulation and by \ref{eq2}, for three different imaging times. The predictions agree in both the high and low intensity limits, and differ for probe intensitites comparable to the saturation intensity. The difference is enhanced with increased imaging time.}  

@@

	\includegraphics[scale=0.57]{figure4}

@@

	\includegraphics[scale=0.57]{figure5}
\caption{The velocity of a single superatom as a function of probe intensity for various imaging times. The dots represent simulation data, while the lines represent analytical solutions.}  

@@

	\subfigure[]{\includegraphics[scale=0.42]{figure6a}}
	\subfigure[]{\includegraphics[scale=0.42]{figure6b}}
\caption{Phase space evolution of an atomic cloud exposed to probe light of $1.2 I_{sat}$. The optical depth is 1.6, and the initial cloud is a gaussian with width a. 10$\mu m$ and b. 1$\mu m$}  

@@

	\includegraphics[scale=0.57]{figure7}

@@

	\includegraphics[scale=0.57]{figure8}
\caption{The optical density as a function of probe intensity for three imaging times. The dots represent experimental data and the lines represent the best fit of simulated data. The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/us. }  

>>>>

	\subfigure[]{\includegraphics*{Picture1c.pdf}}

@@

	\includegraphics*{figure1.pdf}

@@

	\includegraphics*{figure2.pdf}

@@

	\includegraphics{figure3.pdf}
\caption{Optical densities as a function of probe intensity as predicted by the simulation (blue dots) and by eq.[\ref{eq2}] (green lines), for three different imaging times. The predictions agree in both the high and low intensity limits, and differ for probe intensitites comparable to the saturation intensity. The difference is enhanced with increased imaging time.}  

@@

	\includegraphics{figure4.pdf}

@@

	\includegraphics{figure5.pdf}
\caption{The velocity of a single superatom as a function of probe intensity for various imaging times. Simulation data (dots) and analytical solutions (lines) are in good agreement.}  

@@

	\subfigure[]{\includegraphics{figure6a.pdf}}
	\subfigure[]{\includegraphics{figure6b.pdf}}
\caption{Phase space evolution of an atomic cloud exposed to probe light of $1.2 I_{sat}$. We have used $\Delta \rm{v}=\rm{v} -\left< \rm{v}(t) \right>$  and $\Delta \rm{z}=\rm{z}-\left< \rm{z}(t) \right>$, subtracting out the center of mass position and velocity of the cloud. The optical depth is 1.6, and the initial cloud is a gaussian with width a.10$\mu m$ and b.1$\mu m$.}  

@@

	\includegraphics{figure7.pdf}

@@

	\includegraphics{figure8.pdf}
\caption{The optical density as a function of probe intensity for three imaging times: $t=40\mu \rm{s}$ (blue),  $t=75\mu \rm{s}$ (green),  $t=100\mu \rm{s}$ (red). The dots represent experimental data and the lines represent the best fit of simulated data. The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/us. }  
